Quality of Service with Software Defined Network.

### 2017-03-06 report/paper.tex
merge with andrea

\section{Needs and Gools}\label{sec:obb} %obbiettivi ed esigenze controllare 
The main gool of this experience is to develop a small SDN network in a lab with real hardware
in orther to understood come a livello pratico si possa implementare  a QoS service in a SDN scenarois.
Our network have to manage traffic with a global scope, in order to evolve in base on different parameters.
Inoltre the SDN network need to interact with world wide web efficently.
%correggere
  \subsection{Adaptability of the network}
  Made Network Adaptable means poter dirottare il traffico in real time to ensure a lot of demands. For example we have to avoid link congestion, 
  but we can prefer reroute some hosting traffic to peggiorare it's performance because of it's evil traffic.
  To reach this gools we need to have a global knowledge on the network and we have to modify the routing table on every routerboard with a 
  global scope.
  The performance of a single connection and entire network can ensure various type of metrics.
  In order to assicurare queste ci serve una struttura dati che si aggiorna costantemente nella quale immagazzinare le statistiche dei link 
  in modo all'occorrenza di trovare il percordo migliore per ogni singolo flusso dati.
  \#TODO MATTEO
  \subsection{Exterior comunication}
  \#TODO pitt

@@

\section{Conclusions}\label{sec:conclusion}
Conclusions are a superbrief summary of what has been done and highlighting of the "take home message"

\#TODO

>>>>

\section{Needs and Gools}\label{sec:obb} %obbiettivi ed esigenze controllare 
The main gool of this experience is to develop a small SDN network in a lab with real hardware
in orther to understood come a livello pratico si possa implementare  a QoS service in a SDN scenarois.
Our network have to manage traffic with a global scope, in order to evolve in base on different parameters.
Inoltre the SDN network need to interact with world wide web efficently.
%correggere
  \subsection{Adaptability of the network}
  Made Network Adaptable means poter dirottare il traffico in real time to ensure a lot of demands. For example we have to avoid link congestion, 
  but we can prefer reroute some hosting traffic to peggiorare it's performance because of it's evil traffic.
  To reach this gools we need to have a global knowledge on the network and we have to modify the routing table on every routerboard with a 
  global scope.
  The performance of a single connection and entire network can ensure various type of metrics.
  In order to assicurare queste ci serve una struttura dati che si aggiorna costantemente nella quale immagazzinare le statistiche dei link 
  in modo all'occorrenza di trovare il percorso migliore per ogni singolo flusso dati.
  \#TODO MATTEO
  \subsection{Exterior comunication}
  \#TODO pitt

@@

\section{Conclusions}\label{sec:conclusion}
Conclusions are a superbrief summary of what has been done and highlighting of the "take home message"
ehi
\#TODO
